On exponential sums arising from the classical doubling method

### 2025-03-01 paper.tex
More corrections

Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a character. For an irreducible representation  $\tau$ of $\GL_k\left(\finiteField\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor}}.$$
Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.

>>>>

Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character. For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor}}.$$
Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
